Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-09-24 main_new.tex
Front end updates

% Template for the submission to:
%   The Annals of Probability           [aop]
%   The Annals of Applied Probability   [aap]
%   The Annals of Statistics            [aos] 
%   The Annals of Applied Statistics    [aoas]
%   Stochastic Systems                  [ssy]
%
%Author: In this template, the places where you need to add information
%        (or delete line) are indicated by {???}.  Mostly the information
%        required is obvious, but some explanations are given in lines starting
%Author:
%All other lines should be ignored.  After editing, there should be
%no instances of ??? after this line.

% use option [preprint] to remove info line at bottom
% journal options: aop,aap,aos,aoas,ssy
% natbib option: authoryear

@@

\input{commands.tex}
\usepackage{amsmath}
\usepackage{pstricks,pst-grad}
\usepackage{graphicx}
\usepackage{floatrow}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\floatsetup[table]{capposition=top}
% \usepackage{subfig}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}

%\usepackage[tableposition = top]{caption} % captions
\usepackage{booktabs}                     % horizontal lines in tables

@@

% provide arXiv number if available:
%\arxiv{arXiv:0000.0000}

@@

% indicate corresponding author with \corref{}
% \author{\fnms{John} \snm{Smith}\corref{}\ead[label=e1]{smith@foo.com}\thanksref{t1}}
% \thankstext{t1}{Thanks to somebody} 
% \address{line 1\\ line 2\\ printead{e1}}
% \affiliation{Some University}
\begin{aug}
\author{\fnms{Trygve Olav} \snm{Fossum}\thanksref{a}, \corref{} \ead[label=e1]{trygve.o.fossum@ntnu.no}}
\author{\fnms{Jo} \snm{Eidsvik}\thanksref{b}, \ead[label=e2]{jo.eidsvik@math.ntnu.no}}
\author{\fnms{David} \snm{Ginsbourger}\thanksref{c}, \ead[label=e3]{david.ginsbourger@idiap.ch}}
\and
\author{\fnms{Kanna} \snm{Rajan}\thanksref{d}. \ead[label=e4]{kanna.rajan@ntnu.no}}

\address{Department of Marine Technology\\ Trondheim, Norway\printead{e1}}
\affiliation[a]{Department of Marine Technology, The Norwegian University of Science and Technology (NTNU) \&\\ Centre for Autonomous Marine Operations and Systems (AMOS), Trondheim, Norway.}

\address{Department of Mathematical Sciences \printead{e2}}
\affiliation[b]{Department of Mathematical Sciences, NTNU.}

\address{Idiap \printead{e3}}
\affiliation[c]{Uncertainty Quantification and Optimal Design group, Idiap Research Institute, Martigny, Switzerland.}

\address{Department of Engineering Cybernetics,\printead{e4}}
\affiliation[d]{Department of Engineering Cybernetics, NTNU \&\\ Underwater Systems and Technology Laboratory, Faculty of Engineering, University of Porto, Portugal.}

>>>>

@@

\input{commands.tex}
\usepackage{amsmath}
\usepackage{pstricks,pst-grad}
\usepackage{graphicx}
\usepackage{floatrow}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\floatsetup[table]{capposition=top}
\usepackage{subfigure}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}                     % horizontal lines in tables

@@

@@

\begin{aug}
\author{\fnms{Trygve Olav} \snm{Fossum}\thanksref{a,b}, \corref{} \ead[label=e1]{trygve.o.fossum@ntnu.no}}
\author{\fnms{Jo} \snm{Eidsvik}\thanksref{c}, \ead[label=e2]{jo.eidsvik@math.ntnu.no}}
\author{\fnms{David} \snm{Ginsbourger}\thanksref{d}, \ead[label=e3]{david.ginsbourger@idiap.ch}}
\and
\author{\fnms{Kanna} \snm{Rajan}\thanksref{e,f}. \ead[label=e4]{kanna.rajan@ntnu.no}}

\address{Department of Marine Technology\\ Trondheim, Norway\printead{e1}}
\affiliation[a]{Department of Marine Technology, The Norwegian University of Science and Technology (NTNU), Trondheim, Norway.} 
\affiliation[b]{Centre for Autonomous Marine Operations and Systems (AMOS).}

\address{Department of Mathematical Sciences \printead{e2}}
\affiliation[c]{Department of Mathematical Sciences, NTNU.}

\address{Idiap \printead{e3}}
\affiliation[d]{Uncertainty Quantification and Optimal Design group, Idiap Research Institute, Martigny, Switzerland.}

\address{Department of Engineering Cybernetics,\printead{e4}}
\affiliation[e]{Department of Engineering Cybernetics, NTNU}
\affiliation[f]{Underwater Systems and Technology Laboratory, Faculty of Engineering, University of Porto, Portugal.}
